Unprepared colonoscopy identifies microbiota specific to the proximal and distal

### 2017-07-26 submission/manuscript.Rmd
fixed some inline values

#### Random Forest classification models identify important OTUs on each side
To identify OTUs that were distinct at each biogeographical site, we constructed several Random Forest models trained using OTU abundances. We built the first model to classify the lumen versus mucosal samples for the proximal and distal sides, independently (Figure 4A). The constructed model used ((Xopt)) features for the proximal and ((Xopt)) for the distal. The models performed well when classifying these samples (`r round(cv10f_roc_proximal_bs$auc,3)` and `r round(cv10f_roc_distal_bs$auc, 3)`, respectively). The OTUs that were most predictive of each site are identified by their greatest mean decrease in accuracy when removed from the model. For distinguishing the proximal lumen and mucosa, OTUs from the _Bacteriodes_, _Actinomyces_, _Psuedomonas_ and two OTUs from the _Enterobacteraceae_ genera were differentially abundant (Figure 4B). The model classifying the distal lumen and mucosa identified OTUs from _Turicibacter_, _Finegoldia_, _Peptoniphilus_ and two OTUs from the _Anaerococcus_ genera that could distinguish lumen from mucosal samples (Figure 4C). These results indicate that there are fine differences between the different sites of the colon, and that these can be traced down to specific OTUs on each side.

Next, we built a model to differentiate the proximal and distal lumenal samples. The model performed best when distinguishing the proximal versus distal mucosa (Figure 5A, AUC = 0.912) compared to the proximal versus distal lumen (AUC = 0.755). These models were able to explain ((X%)) of the variance, respectively. OTUs that were differentially abundant between the distal and proximal mucosa included members of the _Porphyromonas_, _Murdochiella_, _Finegoldia_, _Anaerococcus_ and _Peptoniphilus_ genera (Figure 5B). Differentially abundant OTUs of the proximal and distal lumen included three OTUs of the _Bacteroides_ genus, a _Clostridium IV_ OTU and an _Oscillibacter_ OTU (Figure 5C). This analysis found that some of the same OTUs that are distinct between the mucosa and lumen also helped to differentiate between the two sides- such as _Anaerococcus_ and _Finegoldia_.

>>>>

#### Random Forest classification models identify important OTUs on each side
To identify OTUs that were distinct at each biogeographical site, we constructed several Random Forest models trained using OTU abundances. We built the first model to classify the lumen versus mucosal samples for the proximal and distal sides, independently (Figure 4A). The constructed model used `r length(2:ncol(aucrf_data_proximal_bs))` features for the proximal and `r length(2:ncol(aucrf_data_distal_bs))` for the distal. The models performed well when classifying these samples (`r round(cv10f_roc_proximal_bs$auc,3)` and `r round(cv10f_roc_distal_bs$auc, 3)`, respectively). The OTUs that were most predictive of each site are identified by their greatest mean decrease in accuracy when removed from the model. For distinguishing the proximal lumen and mucosa, OTUs from the _Bacteriodes_, _Actinomyces_, _Psuedomonas_ and two OTUs from the _Enterobacteraceae_ genera were differentially abundant (Figure 4B). The model classifying the distal lumen and mucosa identified OTUs from _Turicibacter_, _Finegoldia_, _Peptoniphilus_ and two OTUs from the _Anaerococcus_ genera that could distinguish lumen from mucosal samples (Figure 4C). These results indicate that there are fine differences between the different sites of the colon, and that these can be traced down to specific OTUs on each side.

Next, we built a model to differentiate the proximal and distal lumenal samples. The model performed best when distinguishing the proximal versus distal mucosa (Figure 5A, `r round(cv10f_roc_muc$auc,3)`) compared to the proximal versus distal lumen (`r round(cv10f_roc_lum$auc, 3)`). These models were able to explain ((X%)) of the variance, respectively. OTUs that were differentially abundant between the distal and proximal mucosa included members of the _Porphyromonas_, _Murdochiella_, _Finegoldia_, _Anaerococcus_ and _Peptoniphilus_ genera (Figure 5B). Differentially abundant OTUs of the proximal and distal lumen included three OTUs of the _Bacteroides_ genus, a _Clostridium IV_ OTU and an _Oscillibacter_ OTU (Figure 5C). This analysis found that some of the same OTUs that are distinct between the mucosa and lumen also helped to differentiate between the two sides- such as _Anaerococcus_ and _Finegoldia_.
